### 2014-02-28 paper/concrete.tex

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated.  In particular, it is not
sound to share references to a heap cell between different tasks.
Otherwise, information can be trivially leaked by copying
secret data into a reference in one task, and then
reading it again by a another task with a lower label.
Clearly, we cannot
modify the semantics in arbitrary ways if we are hoping to preserve
non-interference, but how can we know if our changes to the abstract
semantics preserve non-interference?
The intention of our single heap implementation was to be more efficient
by using one global heap, but conceptually maintain isolation between
task by not allowing sharing of references between tasks.
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

\Red{We really should not use red/blue here.  I suggest we just use primes instead of colors here.}
\begin{definition}[Isomorphism of information-flow control languages]
  A language \con{|(C, .->, erasef l)|} is \textit{isomorphic} to a
  language \abs{|(iC, .->, erasef l)|} if there exist total functions |f
  : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC| |finv
  .. f = idf iC|.  Furthermore, |f| and |finv| are functorial (e.g. if
  $\abs{x\ R\ y}$ then $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
  $l$-equivalences and |.->|.

  If we weaken this restriction such that |finv| does
  not have to be functorial over |.->|, we call the
  language \con{|(C, .->, erasef l)|} \textit{weakly isomorphic} to
  \abs{|(iC, .->, erasef l)|}.
\end{definition}

>>>>

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated.  In particular, it is not
sound to share references to a heap cell between different tasks.
Otherwise, information can be trivially leaked by copying
secret data into a reference in one task, and then
reading it again by a another task with a lower label.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation was to be more efficient
by using one global heap, but conceptually maintain isolation between
task by not allowing sharing of references between tasks.
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

% con no-prime red target
% abs prime blue ifc

\begin{definition}[Isomorphism of information-flow control languages]
  A language |(C, .->, erasef l)| is \textit{isomorphic} to a
  language |(C', tarrow', erasefp l)| if there exist total functions |f
  : C -> C'| and |finv : C' -> C'| such that |f .. finv = idf C| |finv
  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g. if
  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
  $l$-equivalences and |.->|.

  If we weaken this restriction such that |finv| does
  not have to be functorial over |.->|, we call the
  language |(C, .->, erasef l)| \textit{weakly isomorphic} to
  |(C', tarrow', erasefp l)|.
\end{definition}
